---
title: "Mute date"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mute date}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Here, I will show how to use the `mute_date()` function.

Just a couple simple questions, at first:

1. What should the API look like?

1. What should the function do?

For the API, I am imagining something like this:

```r
mute_date(data = electricity, duration_ref = dhours(2))
```

Argument        | Type       | Description
--------------- | ---------- | -------------------------------------------------
`data`          | data frame | tidytemps-compliant data frame
`duration_ref`  | numeric    | number of seconds after local midnight when a date-batch starts

There is a deeper idea here about batches. We take a one-dimensional time-series and and "bend" it into two dimensions: say `batch` and `batch_index`. In this case, we may think of `date` and `date_index`.

The function returns a modified copy of `data`, adding two columns:

Variable        | Type       | Description
--------------- | ---------- | -------------------------------------------------
`date`          | Date       | date, using local timezone, at the start of the date-batch
`date_index`    | double     | time (duration) since the local midnight corresponding to `date` (s)


Let's try this out:

```{r}
library("tidytemps")
library("lubridate")
library("tidyverse")
library("hms")
```

```{r}
glimpse(electricity)
```

```{r}
electricity_date <-
  electricity %>%
  mute_date(dhours(2)) 

glimpse(electricity_date)
```

```{r}
electricity_date %>%
  ggplot(aes(x = as.hms(date_index), y = consumption_rate)) +
  geom_line(aes(color = as.factor(date))) 
```
